%-------------------------
% Resume in Latex
% Author : Harshibar
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[scale=0.90,lf]{FiraMono}

\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{%
  \bfseries \vspace{0pt} \raggedright \large%
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-6pt}]

\newcommand{\resumeItem}[1]{%
  \item\small{#1 \vspace{-1pt}}%
}

\newcommand{\resumeSubheading}[4]{%
  \vspace{-1pt}\item
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
    \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
  \end{tabular*}\vspace{-4pt}%
}

\newcommand{\resumeSubSubheading}[2]{%
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}%
}

\newcommand{\resumeProjectHeading}[2]{%
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    #1 & {\color{dark-grey}} \\
  \end{tabular*}\vspace{-4pt}%
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}%
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}%
\newcommand{\resumeItemListStart}{\begin{itemize}}%
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}%

\color{text-grey}

\begin{document}

\begin{center}
    \textbf{\Huge Thorger S. Jansen} \\ \vspace{5pt}
    \small \faPhone* \texttt{+49 1575 7214751} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt} \texttt{CV@ThorgerJansen.de} \hspace{1pt} $|$ 
%    \hspace{1pt} \faYoutube \hspace{2pt} \texttt{harshibar} \hspace{1pt} $|$
    \hspace{1pt} \faMapMarker* \hspace{2pt}\texttt{Bochum, Germany}
    \\ \vspace{-3pt}
\end{center}

\section{RECENT WORK}
A full CV with more details is available at: \href{https://thorgerjansen.de}{https://thorgerjansen.de}.
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://sec-consult.com/}{SEC Consult Group}}{Oct. 2023 -- Present}
      {Associate Security Consultant}{Bochum, DE}
      \resumeItemListStart
      \resumeItem{Security audits, continuous testing, and code reviews for government agencies, international organizations, leading private-sector companies, and critical infrastructure.}
       \resumeItem{Conducted various research projects (e.g., vulnerabilities in bossware), leading to multiple CVEs and coordinated responsible disclosure processes with vendors.}
       \resumeItem{Direct client communication, reporting, quality assurance, and continuous improvement of delivery quality.}
      \resumeItemListEnd
      
      \resumeSubheading
      {\href{https://www.joinef.com/}{Entrepreneurs First}}{Jun 2025 -- Oct 2025}
      {Resident / Founder}{San Francisco, US}
      \resumeItemListStart
      \resumeItem{Founded a company in the U.S. market that used ML to assist elderly individuals and care facilities, predicting well-being outcomes, including Alzheimer's detection up to 10 years in advance.}
      \resumeItemListEnd

      \resumeSubheading
      {\href{https://www.inf.bi.ruhr-uni-bochum.de/}{Chair of Computing in Engineering, Ruhr University Bochum}}{Sep 2020 -- Sep 2023}
      {Student Assistant}{Bochum, DE}
      \resumeItemListStart
      \resumeItem{Worked on various programming and research projects with well-known industry partners such as Hochtief, including developing augmented reality applications for HoloLens and machine learning algorithms for the Boston Dynamics Spot.}
      \resumeItem{Supported teaching the Web Engineering course, including planning and creating course content.}
      \resumeItem{Published a paper at the Forum Bauinformatik 2023.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section {EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.ruhr-uni-bochum.de/}{Ruhr University Bochum}}{2018 -- 2026}
     {Bachelor of Science (B. Sc.) IT Security / Information Engineering}{Bochum, DE}
    \resumeItem{Achieved the highest grade (99/100) in Blockchain Security and received a scholarship; attended lectures in cryptography, electrical engineering, systems, computer science, mathematics, network security, and related fields.}
    \resumeSubheading
      {\href{https://gym-eickel.de/}{Gymnasium Eickel}}{2010 -- 2018}
     {Abitur \O1.7  (Scale 1-6, lower is better.)}{Herne, DE}
  \resumeSubHeadingListEnd
  
\section{PUBLICATIONS}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://doi.org/10.13140/RG.2.2.31236.59520}{Improving LLMs front-running detection capabilities (2.0)}}{2025}
     {Bachelor's Thesis}{10.13140/RG.2.2.31236.59520}
    \resumeSubheading
      {\parbox[t]{0.7\textwidth}{\href{https://doi.org/10.13154/294-10121}{An overview of outdoor and indoor navigation in regard to the use of\\existing standards}}}{2023}
      {Conference Paper 34. Forum Bauinformatik}{10.13154/294-10121} 
\resumeSubHeadingListEnd

\section{MISC}
\begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Certifications} {Multiple certifications including OSWA, CBBH, AZ-900, and others.}
\vspace{1pt} \\
     \textbf{CVEs} {Identified 19 CVEs across various software systems, including FlexNow, an electronic examination management system widely used by German universities.}\vspace{1pt} \\
     \textbf{Honors and Awards}{Multiple honors and awards, including recognition in the Bundeswehr Hall of Fame, the VDPBw Coin, Rotary Youth Leadership Awards, and other IT security-related distinctions.}
\vspace{1pt} \\
     \textbf{Voluntary Work}{Engaged in voluntary work focused on accessibility and politics, including serving as Department Head of the Autonomous Department for People with Disabilities and All Impairments at AStA Ruhr University Bochum.}
\vspace{1pt} \\
     \textbf{Entrepreneur}{Experience founding companies, including a startup in Silicon Valley.}
    }}
 \end{itemize}

\end{document}